Best Practices for Alchemical Free Energy Calculations [Article v \versionnumber]

### 2020-11-28 paper/manuscript.tex
Updates from Overleaf

\begin{figure}
    \includegraphics[width=0.95\linewidth]{figures/fig1_what_is_alchemy/Figure.pdf}   
    \caption{\textbf{Illustration of common types of free energies differences that can be calculated using alchemical free energy methods.} \textbf{A}: Change in free energy due to a conformational change of the molecule across a high barrier. \textbf{B}: Partition coefficient such as $\log P$ or $\log D$ depend on a change in free energy between different phases; here, as an example the partition coefficient between methanol and water is shown. \textbf{C}: Free energy difference associated with the insertion of a molecule into a membrane. \textbf{D}: Effect of mutations of protein or host residues on free energies of binding. \textbf{E}: Absolute free energies of binding of a small molecule to a host (e.g. protein), \textbf{F}: Relative free energy of binding of one molecule with respect to another, here toluene and benzyl alcohol.
    \label{fig:fig_what_is_alchemy}
    }
\end{figure}

@@

In contrast, in a dual topology alchemical free energy calculation, no atoms are allowed to change type~\cite{Boresch:1999:J.Phys.Chem.A, shirts2012best}. This means that the benzene to benzyl alcohol transformation involves starting with benzene plus the non-interacting dummy atoms making up the hydroxy methyl group, then passing through an intermediate state where some atoms are partially interacting--- particularly, those atoms which are becoming dummy atoms or ceasing to be dummy atoms~\cite{mobley2014blind}. The transformation finally culminates in a state where benzyl alcohol is present along with the additional dummy atom which was previously a corresponding hydrogen of the benzene. Fig.~\ref{fig:fig_topology}'s right branch depicts how such a dual topology works.

@@

It is however important to note that different packages also differ in how they handle implementation of alchemical transformations, making it difficult to give rules of thumb concerning specific efficient transformations which work equally well across simulation packages. Thus we are hesitant to recommend best practices within specific software packages at point in time, although any good transformation pathway will conform to the guidelines we have outlined above.

>>>>

\begin{figure}
    \includegraphics[width=0.95\linewidth]{figures/fig1_what_is_alchemy/Figure.pdf}   
    \caption{\textbf{Illustration of common types of free energies differences that can be calculated using alchemical free energy methods.} \textbf{A}: Change in free energy due to a conformational change of the molecule across a high barrier. \textbf{B}: Partition coefficient such as $\log P$ or $\log D$ depend on a change in free energy between different phases; here, as an example the partition coefficient between methanol and water is shown. \textbf{C}: Free energy difference associated with the insertion of a molecule into a membrane. \textbf{D}: Effect of mutations of protein or host residues on free energies of binding. \textbf{E}: Relative free energy of binding of one molecule with respect to another, here toluene and benzyl alcohol, \textbf{F}: absolute free energies of binding of a small molecule to a host (e.g. protein).
    \label{fig:fig_what_is_alchemy}
    }
\end{figure}

@@

In contrast, in a dual topology alchemical free energy calculation, no atoms are allowed to change type~\cite{boresch1999rolea, shirts2012best}. This means that the benzene to benzyl alcohol transformation involves starting with benzene plus the non-interacting dummy atoms making up the hydroxy methyl group, then passing through an intermediate state where some atoms are partially interacting--- particularly, those atoms which are becoming dummy atoms or ceasing to be dummy atoms~\cite{mobley2014blind}. The transformation finally culminates in a state where benzyl alcohol is present along with the additional dummy atom which was previously a corresponding hydrogen of the benzene. Fig.~\ref{fig:fig_topology}'s right branch depicts how such a dual topology works.

@@

It is however important to note that different packages also differ in how they handle implementation of alchemical transformations, making it difficult to give rules of thumb concerning specific efficient transformations which work equally well across simulation packages. Thus we are hesitant to recommend best practices within specific software packages at this point in time, although any good transformation pathway will conform to the guidelines we have outlined above.
